Dysregulation of Cerebral Hemoglobin Content in Malawian Children with Malaria

### 2021-05-13 figures.Rmd
change table 1 title
change PC vector magnitude

### Table 1: Summary of hematological data by patient group

@@

  # plot variables
  geom_point(data = df_vars, aes(x = PC1*10, y = PC2*10)) +
  geom_text_repel(data = df_vars, aes(x = PC1*10, y = PC2*10, label = variable, size = 10), show.legend = FALSE) +
  geom_segment(data = df_vars, aes(x = 0, y = 0, xend = PC1*10, yend = PC2*10), arrow = arrow()) +

>>>>

### Table 1: Summary of clinical data by patient group

@@

  # plot variables
  geom_point(data = df_vars, aes(x = PC1*5, y = PC2*5)) +
  geom_text_repel(data = df_vars, aes(x = PC1*5, y = PC2*5, label = variable, size = 10), show.legend = FALSE) +
  geom_segment(data = df_vars, aes(x = 0, y = 0, xend = PC1*5, yend = PC2*5), arrow = arrow()) +
